HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
misc
figure

\paragraph{UCCA Annotation.}
We begin by creating UCCA annotations for the source sentence, following the
UCCA guidelines\footnote{All UCCA-related resources can be found
  here: \url{http://www.cs.huji.ac.il/~oabend/ucca.html}}.
Let $L$ be the set of possible UCCA labels.
Given a sentence $s = (w_1, \ldots,w_n)$, its UCCA annotation is a DAG $G=(V,E,\ell)$,
where $\ell: V \rightarrow L$, and where $W = \{w_1,\ldots,w_n\}$ correspond to the leaves of $G$.
For every node $v \in V$, we define its {\it yield} $yld(v)$ as $v$'s descendants in $W$.
The semantic units for a sentence $s$ induced by the annotation $G$,
is the set of yields of nodes in $V$. %We denote it with $Units(s)$ for brevity.
We note that the translation is not UCCA-annotated.

@@

\paragraph{Translation Evaluation.}
The basic strategy for computing HUME is to traverse
the semantic units of the source sentence, and to mark the extent to which
they have been correctly translated. As semantic units correspond to the
semantic relations expressed in the text and the inter-relations between them,
HUME effectively aggregates the judgements of the users into a composite score.

>>>>

\paragraph{UCCA Annotation.}
We begin by creating UCCA annotations for the source sentence, following the
UCCA guidelines\footnote{All UCCA-related resources can be found
  here: \url{http://www.cs.huji.ac.il/~oabend/ucca.html}}.
Let $L$ be the set of possible UCCA labels.
Given a sentence $s = (w_1, \ldots,w_n)$, its UCCA annotation is a DAG $G=(V,E,\ell)$,
where $\ell: V \rightarrow L$, and where $W = \{w_1,\ldots,w_n\}$ correspond to the leaves of $G$.
For every node $v \in V$, we define its {\it yield} $yld(v)$ as $v$'s descendants in $W$.
The semantic units for a sentence $s$ according to $G$
is the set of yields of nodes in $V$. 
We note that the translation is not UCCA-annotated.

@@

\paragraph{Translation Evaluation.}
The basic strategy for computing HUME is to traverse the semantic units
of the source sentence, which correspond to the different arguments and relations expressed
in the text, and to mark the extent to which they have been correctly translated.
HUME aggregates the judgements of the users into a composite score, 
which reflects the overall extent to which the semantic content of $s$ is preserved in $t$.
